# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015]. ddd aaa [@davison1997bootstrap]

```{r}
library(boot)

mouse.c <- scan("http://www.rohan.sdsu.edu/~babailey/stat672/mouse.c.data")
mouse.t <- scan("http://www.rohan.sdsu.edu/~babailey/stat672/mouse.t.data")


y<-mouse.c
sd(y)

n.c<-length(mouse.c)

B<-100000

thetahat.c<-mean(mouse.c)
sehat.c<-sd(mouse.c)*sqrt((n.c-1)/n.c^2)

theta.boot<-rep(0,B)

Zb<-rep(0,B)
Zbt<-rep(0,B)
for(b in 1:B){

	yboot<-sample(mouse.c,size=n.c,rep=T)
	thetahat.boot<-mean(yboot)
	sehat.boot<-sd(yboot)*sqrt((n.c-1)/n.c^2)

	Zb[b]<-(thetahat.boot-thetahat.c)/sehat.c

	Zbt[b]<-(thetahat.boot-thetahat.c)/sehat.boot

	theta.boot[b]<-thetahat.boot

}
hist(theta.boot,xlab=expression(theta),br=seq(0,130,by=5),col='gray',main=expression(paste('Bootstrap resamples of ',hat(theta))));box()
abline(v=thetahat.c,col='red',lwd=2)

abline(v=quantile(theta.boot,prob=c(0.025,0.975)),col='red',lty=2,lwd=2)

alpha<-0.05
qs<-quantile(Zb,prob=c(1-alpha/2,alpha/2))
qst<-quantile(Zbt,prob=c(1-alpha/2,alpha/2))
abline(v=thetahat.c-qst*sehat.c,col='green',lty=2,lwd=2)
abline(v=thetahat.c-qs*sehat.c,col='blue',lty=2,lwd=2)
```

