# Simulations

In this chapter you'll learn how to conduct a simulation study. The word _simulation_ gets thrown around alot as a trivial concept, though I have found that this term is often either misused by epidemiologists or abused by statisticians. A source of this confusion arises from the fact that it is not well defined. This is not by accident. A simulation study has so many moving parts that it would be impossible to characterize in a single word. However, there are some common underlying themes behind simulation studies. For this reason, the main focus here will be on creating a general roadmap for conducting these types of analyses, that can be applied to your specific setting. 


## What is a simulation study?

Here are some results from a Google Search:

1. A numerical technique for conducting experiments on the computer [@marie]
2. Simulations provide a powerful technique for answering a broad set of methodological and theoretical questions and provide a flexible framework to answer specific questions relevant to one's own research[@hallgren2013conducting]

I prefer the second definition because it speaks to the generality of simulations. I see simulations in the following way:

```{r, echo=FALSE}
DiagrammeR::mermaid("
graph LR
A((Input 1))-->B{Procedure}
D((Input 2))-->B{Procedure}
E((Input 3))-->B{Procedure}
B-->C[Output 1]
B-->F[Output 1]
B-->G[Output 1]
")
```

In words, you have a **fixed** procedure that takes several _different_ inputs and produces an equal number of outputs. The following toy example illustrates this point:

```{r, echo=-1}
set.seed(123)
f_sample_median <- function(true_mean) {
  x <- rnorm(20, mean = true_mean)
  median(x)
}

(means <- c(1,2,3))

(sample_medians <- sapply(means, f_sample_median))
```

So here, `f_sample_median` is the procedure, `means` is the input, and `sample_medians` is the output:

```{r, echo=FALSE}
DiagrammeR::mermaid("
graph LR
A((1))-->B{f_sample_median}
D((2))-->B
E((3))-->B
B-->C[1.12]
B-->F[1.86]
B-->G[2.96]
")
```



