--- 
title: "Biostatistics in R"
author: "Sahir Rai Bhatnagar"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::gitbook:
    highlight: tango
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: sahirbhatnagar/biosR
description: "These are a collection of tutorials that I have found useful in statistical applications."
---

# Prerequisites

## Install R and RStudio

All examples in this book are run in an [R](https://cran.r-project.org/) environment. You also need a recent version of [RStudio](https://www.rstudio.com/products/rstudio/download/preview/), which is a software application that facilitates how you interact with `R`. It is developed by data enthusiasts who consider statistics to be more than just simulations, formulas and proofs. RStudio emphasizes the following: 

1. **Version control**:  [Why I should use version control](http://stackoverflow.com/questions/1408450/why-should-i-use-version-control) especially for the [solo data analyst](http://stackoverflow.com/questions/2712421/r-and-version-control-for-the-solo-data-analyst).

2. **Reproducible research**: seamless integration with [RMarkdown](http://rmarkdown.rstudio.com/) for creating [dynamic documents](http://yihui.name/knitr/) and presentations

3. **Creating R Packages**: seamless integration with the [devtools](https://github.com/hadley/devtools) package for creating software that implements your statistical method or analysis. 



## R Packages

The following packages will be called upon at some point, so please install them before getting started with the tutorials. Enter the following command in `R`:

```{r eval=FALSE, echo=TRUE}
install.packages(c("knitr","data.table", "rmarkdown", "dplyr", "purrr", 
                   "tidyr", "ggplot2", "pwr", "glmnet", "boot","DAAG"))
```


## Background Reading

The greatest thing about `R` is that there are so many people out there willing to help you. `R` users are constantly writing tutorials and creating packages to make your analysis tasks easier. Here is a very targeted list that I suggest reading prior to starting the tutorials

1. [Writing Functions](http://r4ds.had.co.nz/functions.html) 
2. [`for` loops](http://r4ds.had.co.nz/iteration.html)
3. [`apply` vs. `for`](https://kbroman.wordpress.com/2013/04/02/apply-vs-for/)

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', 'data.table', 'dplyr',
  'purrr', 'boot', 'ggplot2', 'DiagrammeR','glmnet','DAAG'), 'packages.bib')
```
